# Review of Literature

I review the literature for what has been studied and what is yet unknown regarding what supports for professional learning ECEs seek during induction, if any; from whom; and how, if at all, they use social media with the intention of seeking supports and connections. This review examines two bodies of research that inform this inquiry: research on teacher induction and research on educators’ use of social media. Although these two areas of scholarship would seem to be potentially related, to date they are almost entirely disparate. I structure this review with sections suggested by the PLN framework: supports for professional learning, reasons for these supports, and interpersonal connections as sources of supports.

## Teacher Induction

The teacher induction literature has often conceptualized induction supports as formal, top-down professional development programs offered by schools and districts. The specifics of these induction supports are important because, as Ronfeldt and McQueen (2017) argued, the quality of induction supports is likely at least as important as the number of supports, if not more so. In addition, this body of research has argued that induction supports should be targeted, systematic, and structured (Kang & Berliner, 2012; Zhukova, 2018).

**Formal induction programs.** The literature describes several types of supports that teacher induction programs offer ECEs, both locally and remotely. In a local context, skills and knowledge are offered through mentoring relationships as well as through seminars and workshops (Fantilli & McDougall, 2009; Kang & Berliner, 2012; Ronfeldt & McQueen, 2017). Collaborative work times provide assistance with teacher planning (Fantilli & McDougall, 2009; Kang & Berliner, 2012; Ronfeldt & McQueen, 2017). Finally, help with classroom management and differentiation of instruction is offered through providing extra classroom assistance to ECEs (Kang & Berliner, 2012). The nature of these programs varies, with some being scheduled (e.g., workshops) and others just-in-time and on-demand (e.g., mentors, classroom assistance).

Although not nearly as common as local, formal induction programs, the idea of connecting new teachers to induction supports beyond the local context has been considered for nearly 25 years. An early example was Singletary and Anderson’s (1995) book chapter on computer-mediated teacher induction. Putnam and Borko (2000) described how the Internet can aid new teachers in the ongoing process of learning to teach “by providing new avenues to access to distributed expertise” (p. 11), but they also raised a number of cautions, such as: the potential lack of critical reflection in online communities, the impact of virtual learning communities on local connections, and the overall need to support ECEs to engage in productive online discourse about teaching and learning. More recently, Alemdag and Erdem (2017) designed an “e-mentoring” program for ECEs in Turkey that used both asynchronous (e.g., discussion forums, blogs) and synchronous (e.g., video conferencing) communication tools to connect mentors and new teachers regardless of geographic location in the country. They concluded that e-mentoring could be an effective support for ECEs if careful attention is given to the recruitment of participants and design of communication. Finally, März and Kelchtermans (2020) described ECEs’ existing informal, “school-external” networks where they seek support often related to issues (e.g., culture, norms, values, rules) in their school of employment.

**Reasons for offering induction programs.** The teacher induction literature is explicitly focused on the needs of ECEs. Ingersoll and Strong (2011) noted that formal induction programs have helped ECEs transition between being students of teaching to teachers of students. This points to a significant underlying reason for ECEs’ needs: the transition from preparation to practice. ECEs have completed their formal professional preparation and are faced with having primary responsibility for enacting educational practice in a professional setting &mdash; ECEs must adjust to carrying the weight of no longer being a student or apprentice, but being the teacher of record. Three realities for ECEs stand out as related to their induction challenges and underlying reasons *why* they need induction support: everything is new, ECEs are still learning, and ECEs are still developing their professional identities. I unpack these three reasons in the following paragraphs.

First, ECEs’ need for induction support stems from the challenge that everything in their professional lives is new. ECEs are adjusting to new colleagues, administrators, students, curriculum, school culture, and politics (Stanulis, Little, & Wibbens, 2012). Because of this newness, ECEs are not able to work with the same efficiency as their more experienced colleagues, and they end up working a disproportionate amount of time just to get by (Fantilli & McDougall, 2009). The focus of educational practice changes with experience. New teachers are just trying to survive, largely focused on personal concerns and resolving classroom management issues; more experienced teachers are able to start focusing on curriculum and teaching practices; and only later are teachers able to finally focus on long-term thinking and student learning (Thompson, Windschitl, and Braaten, 2013; Zhukova, 2018).

Second, ECEs have been credentialed to teach, but they are still learning and honing their educational practice (Stanulis et al., 2012). Ingersoll (2012) explained that induction programs are built upon the assumption that teaching is a complex practice, with knowledge and skills that can only be fully developed by doing the work. Anderson and Stillman (2013) reviewed the literature and found that a dominant model of preservice teacher learning during their field experience is a *replication* of experienced educators’ practices; the challenge then as PSTs become ECEs in the transition from preparation to practice is to move beyond replication to *recontextualization* of practice appropriate for the ECEs’ specific classroom. Fantilli and McDougall’s (2009) survey study reported ECE challenges such as differentiating instruction to meet the needs of advanced students, communicating with parents, managing time for planning and scheduling, and managing students’ behavior in the classroom. These are skills addressed in preparation programs but not yet mastered by ECEs. 

Third, in addition to developing necessary skills, ECEs are also still forming their *professional identities* as educators &mdash; that is, how they understand themselves in relation to teaching (Cuddapah & Clayton, 2011). The development of professional identity contains both *intrapersonal* and *social* processes. On one hand, professional identity is composed of *values* (i.e., personal beliefs and convictions), which are influenced by past experiences and in turn influence present goals (Wray & Richmond, 2018). Values, experiences, and goals must be understood through an intrapersonal process of self-reflection. On the other hand, Pearce and Morrison (2011) argued that identity development is discursive, occurring through interactions with others &mdash; a social process. Wray and Richmond (2018) explained this in terms of *positioning* &mdash; that is, how an ECE behaves within a teaching community and how the members of that community view them in turn. Both intrapersonal and social processes require intentionality, meaning that professional identity is linked to *agency* &mdash; that is, the ability to take purposeful action (Pearce & Morrison, 2011). Agentic actions are influenced by the intrapersonal elements of an ECEs’ identity: past experiences, beliefs, values, and goals &mdash; all in conjunction with context (Wray & Richmond, 2018).

For instance, a significant challenge for ECEs during induction is reconciling their personal values with competing values held by those in the new context, the school of employment (Thompson et al., 2013; Wray & Richmond, 2018). An ECE’s sense of agency can affect whether or not he or she seeks induction supports or interpersonal connections. In addition, this means that an ECE’s ongoing professional-identity development during induction potentially requires rethinking their beliefs about education (Thompson et al., 2013). Finally, because of differences in identity formation, all ECEs do not develop their professional skills in the same way or at the same pace, instead following varying *trajectories* related to how they embrace and reconcile new ideas about educational practice as they learn on the job (Thompson et al., 2013).

In sum, the induction transition places ECEs in contexts where everything is new, skills are still being developed, and professional identity &mdash; particularly personal values needing to be reconciled with those of the new context &mdash; is in flux. Thus, navigating the induction transition and making choices to seek induction supports require purposeful, agentic action.

**Interpersonal connections.** The literature describes several types of interpersonal connections that formal induction programs help facilitate for ECEs. By far the most discussed relationship in the teacher induction literature is that between ECEs and mentor teachers. Ingersoll and Strong’s (2011) literature review found empirical evidence that mentoring programs had a positive impact on the performance and retention of new teachers, and Ronfeldt and McQueen’s (2017) study added nuance, concluding that not all mentoring relationships or programs are the same. Evertson and Smithey’s (2000) research demonstrated that training mentors lets them offer better help to early-career educators. Stanulis and Floden (2009) found benefit in an intensive form of mentoring that included mentors working closely and collaboratively with early-career educators &mdash; observing teaching, co-planning, and jointly analyzing student work. Finally, Davis and Higdon (2008) described how frequent “just-in-time” assistance from mentors was perhaps the most valuable aspect of the induction support program in their study. In sum, the literature seems to suggest that effective relationships between ECEs and mentors may be planned formally, but also require frequent and potentially informal (i.e., unscripted) interaction.

Research has noted the benefit of ECEs receiving supportive communication from school leadership (Fantilli & McDougall, 2009; Ronfeldt & McQueen, 2017). Thomas, Tuytens, Devos, Kelchtermans, and Vanderlinde (2019) found that principals play a key role in welcoming ECEs and helping to organize induction support structures. Conversely, numerous studies have shown that ECEs name inadequate support from the school administration as one of the main factors for decisions to leave a teaching position (Fantilli & McDougall, 2009; Ingersoll & Strong, 2011).

Although peer learning has perhaps been more thoroughly studied among preservice teachers, Thompson et al. (2013) described ECEs’ ongoing professional learning as potentially occurring in a community of their peers. Fresko and Alhija (2015) found that induction seminars could serve as learning communities for ECEs, offering participants the benefit of emotional support afforded by peers with the same professional status rather than hierarchical relationships. Cuddapah and Clayton (2011) studied such peer learning through a cohort of new teachers from across an urban school district that met together face-to-face every two weeks to learn about issues such as classroom management and identifying teaching resources. Finally, März and Kelchtermans (2020) described ECEs’ school-external networks that included former instructors and classmates from preparation programs, as well as family members. These relationships that were a step removed from the local employment context gave ECEs an outlet to discuss organizational concerns related to their schools.

## Educators’ Use of Social Media

Humphreys (2016) emphasized that social media should be thought of as a set of participatory practices for how people use media socially and publicly; this definition is not bounded by commercial platforms but instead focuses on how a medium is used. In contrast to research on teacher induction &mdash; which has often focused on supports formally organized and offered by districts and school &mdash; research on educators’ use of social media has tended to emphasize how educators have sought professional learning through social media platforms in ways that are self-initiated and informal. However, the social media literature only describes what is done by educators generally, not ECEs, because this body of research has not focused upon the challenges and needs of educators during induction. Some studies have focused on preservice teachers’ use of social media for a course assignment in a preparation program (e.g., Luo & Clifton, 2017), but few studies have focused on how ECEs might use social media to look for help after gaining employment or to navigate the particular challenges of the induction transition. 

Humphreys’ (2016) definition and examples of social media encapsulate what earlier researchers (e.g., Greenhow, Robelia, & Hughes, 2009) titled *Web 2.0* &mdash; online platforms that provide opportunities for a variety of social processes, including social networking, social bookmarking, collaborative knowledge development, and so on. Social media differ from general online platforms or Internet tools because of their affordances for modes of participation that have the potential to be social and public. Social media offer opportunities to contribute as well as interact with content and with others around that content, as has been noted in studies of online affinity spaces (e.g., Gee, 2004; Staudt Willet, Koehler, & Greenhalgh, 2017; Staudt Willet & Carpenter, 2019). Greenhow et al. (2009) tied such features to theories of sociocultural activity and situated learning, noting that learning derives from participation in joint activities, is linked to social practices, and is mediated by artifacts over time.

At their best, social media may offer opportunities for ECEs to experience ongoing professional learning in a *participatory culture* characterized by low barriers to expression and engagement, strong support for creating and sharing, informal mentoring, and a degree of social connectedness amongst contributors (Jenkins, 2009). However, participation inequality has been well-documented in Web 2.0 and social media (e.g., Nielson, 2006; Staudt Willet, 2019), meaning that users participate in drastically different ways, with a small number of participants contributing almost all of the content and forging almost all of the social connections. Most users participate through behaviors often characterized as *lurking* &mdash; that is, being present and watching but not making oneself known by contributing. Because lurkers are actively reading and paying attention &mdash; and may even be sharing what they see with others elsewhere &mdash; Edelmann (2013) argued that this prevalent form of participation would be better characterized as *observing*, a term with less negative connotation. Even if the bulk of social media users are not actively contributing to Jenkins’ (2009) vision of an online participatory culture marked by expression and creation, they are still engaging in a form of *legitimate peripheral participation* (Lave & Wenger, 1991). Lave and Wenger (1991) likened legitimate peripheral participation to *learning through apprenticeship*. This is the process through which newcomers learn to belong and become full participants, which is both a social process as well as one of learning knowledgeable skills.

In sum, even if a social media platform does not appear to host a robust participatory culture, it remains more than an online library or information repository because of its *potential* for users to participate, not just observe &mdash; to contribute, to interact with content (e.g., comment, critique, edit, modify, contextualize), and to connect with others around the content (Greenhow et al., 2009). The issue is less about the technological constraints of the social media platform, and more about agentic action. That is, some level of agency is needed to move from observing to taking chances with contributing, interacting with content, or connecting with others. Thus, as ECEs navigate potentially conflicting messages about what and how to teach from their preparation program, local employment context, and social media platforms, they are faced with issues of professional identity and agency.

**Informal learning opportunities.** Macià and García (2016), in their review of the literature, offered one of the most comprehensive frameworks for the types of practices educators develop as they seek professional development through online communities and networks. These ten practices were: (a) share experiences and reflect on practice, (b) pose or answer questions or ask for help, (c) share teaching materials and resources, (d) generic discussion, (e) emotional support, (f) carry out concrete actions, (g) offer online training sessions, (h) share interests, (i) stimulate and manage participation, and (k) live events participation. Numerous empirical studies have reported findings related to what educators are looking for through their use of social media. For example, in a frequently cited study of educators’ participation in online communities, Hur and Brush (2009) interviewed teachers and found “five reasons why teachers wanted to participate in online communities of teachers: (a) sharing emotions, (b) utilizing the advantages of online environments, (c) combating teacher isolation, (d) exploring ideas, and (e) experiencing a sense of camaraderie” (pp. 290-291).

Prestridge (2019) identified two main purposes of teachers’ social media use from her review of the literature. First, a *people orientation* toward social media means that educators share, collaborate, but also sometimes just lurk (i.e., observe) to learn who’s who in an online space. In contrast, a *content orientation* toward social media means that educators share and gather resources, although sometimes teachers just take without contributing. Prestridge (2019) observed that educators with a people orientation do not always engage with content, and educators with a content orientation do not always engage socially. From these observations, Prestridge (2019) built a new typology of social media use that did not assume either content creation or networking. Instead, her model contained two dimensions: an axis of people orientation (i.e., self versus other) and an axis of content orientation (i.e., taking versus contributing). With this model, Prestridge (2019) described four ways that educators use PLNs: info-consumer (self + taking), info-networker (other + taking), self-seeking contributor (self + contributing), and collaborative contributor (other + contributing, which Prestridge [2019] referred to as a vocationalist). 

Many studies have described learning opportunities related to a people orientation. Xing and Gao (2018) concluded that collaboration was an important factor in educators’ ongoing participation in Twitter #Edchat, possibly because they “valued tweets that focused on generating and co-constructing ideas” (p. 395). Davis (2015) described educators’ knowledge-sharing on Twitter as a type of collaborative inquiry and filtering information, and she reported a sense of belonging that teachers found through Twitter. Rehm and Notten (2016) found that educators continued to form new social ties as they spent more time on Twitter. Chen (2011) also reported a sense of “informal camaraderie” (p. 759) resulting from Twitter use, and other researchers have concluded that educators’ experiences of professional isolation can potentially be alleviated through participation on social media like Twitter (Carpenter & Krutka, 2014; Wesely, 2013). Finally, educators’ use of social media for PLNs has been characterized as seeking and finding a “professional refuge” (Trust et al., 2016, p. 31); that is, a place where educators find encouragement and a restoration of energy for teaching. 

It is important to acknowledge that despite these cited benefits of educators using social media for a people orientation, there are numerous new challenges. First, with more voices offering purported wisdom and expertise, educators generally (and perhaps ECEs specifically) face a challenge of reconciling conflicting messages about what and how to teach. Related to this, with many more people to choose from, the complexity of finding a trusted mentor increases (Fantilli & McDougall, 2009). Second, the ability to bypass time and geographical constraints also blurs the lines between teachers’ professional and personal lives, creating an expectation that teachers are &mdash; or should be &mdash; available and accessible to students, parents, and colleagues outside regular school-day hours (Fox & Bird, 2017; Selwyn, Nemorin, & Johnson, 2017). Third, with so many interpersonal connections, self-serving behaviors are prevalent. Prestridge (2019) defined two such types of social media users: the info-consumer and the self-seeking contributor. The latter user type mirrored my findings of tweet purposes in Twitter #Edchat: almost half of the original content in that hashtag is pointing back to one’s self &mdash; not highlighting the work or others or inviting dialogue. Lantz-Andersson, Lundin, and Selwyn (2018) asked related questions in their literature review covering 20 years of online teacher communities: Are educators working together or working alongside each other? Is participation on social media platforms fostering collaboration or competition? In sum, it is vital to keep in mind that more connections through social media are not inherently beneficial &mdash; the nature and quality of those connections must be examined.

In addition to opportunities related to a people orientation, other empirical studies have described professional learning opportunities related to a content orientation. In their extensive survey study of how and why educators use Twitter, Carpenter and Krutka (2014) reported that 96% of survey respondents had shared and acquired educational resources on Twitter. Similarly, Trust et al. (2016) reported educators’ interpretations of their PLNs as “diverse and multifaceted networks of people, communities, tools, platforms, resources and sites” (p. 31) &mdash; in many cases facilitated by social media platforms. In a separate analysis of the same data, Krutka, Carpenter, and Trust (2016) identified five themes among educators’ PLN use: opportunities to engage, discover, experiment, reflect, and share. Tour (2017) interviewed three teachers and reported similar themes of PLN use: information retrieval, resource aggregation, cooperation, collaboration, reflections, and socializing. Duncan-Howell’s (2010) survey study found that educators wanted to select the content of their professional development, seeking learning through online communities that would relate to classroom practices relevant to their own contexts and situations.

Although social media use may not appear to be directly analogous to offline workshops, educators use social media to develop skills and knowledge much like those offered by formal induction programs. For instance, social media platforms like Pinterest have expanded the scope of where and how curricular materials can be located (Hu, Torphy, Opperman, Jansen, & Lo, 2018), and online discussion boards, like the subreddit r/teachingresources, have been created solely for the purpose of sharing resources, (Staudt Willet & Carpenter, 2019). For planning, Twitter hashtags like #SocialMediaSyllabus and #MarginalSyllabus have been used to share and collaboratively develop teaching syllabi (Greenhow, Gleason, & Staudt Willet, 2019).

As with the benefits and challenges of people connections, it is important to acknowledge that despite these cited benefits of educators using social media to find and access resources, there are also potential challenges that may be introduced. To start, because of the volume of resources available through social media, ECEs may have difficulty finding a relevant resource (a search issue) and feeling confident in its quality. Also, with social media, the scope of resources is worldwide, raising a *local-global tension* where the plethora of available resources must be filtered and adapted to be appropriate for a specific educational context (Jones & Preece, 2006). Finally, some supports offered by formal induction programs, like help with classroom management and differentiation of instruction, may be difficult to access through social media.

**Reasons for seeking supports on social media.** Despite a growing body of research on educators’ use of social media, relatively little work has been done to specifically understand why educators use social media to connect with others. *What* professional learning opportunities educators are looking for has been widely investigated, but deeper *Why?* questions have been less explored. Still, Hur and Brush’s (2009) interview study is an example where participants described a number of external and contextual factors related to why educators participate in online communities. For instance, one interviewee said she shared emotions in the WeTheTeachers online community because “Teaching is a hard profession. We get emotionally involved. It's nice to give and share those emotions with one another” (Hur & Brush, 2009, p. 291). The difficulty of the job meant educators share personal and emotional stories online, and other educators offer emotional support or propose solutions. Hur and Brush’s (2009) participants also described searching for very specific ideas online, as well as utilizing the advantages of online communities specifically because of pressures to appear competent to colleagues in the place of employment &mdash; strangers were preferable confidants in some instances because they would have no bearing on future rehiring decisions. However, educators used large, open Facebook groups for pragmatic advice, not to reflect on their professional practice (Kelly & Antonio, 2016). Kelly and Antonio (2016) speculated that this may be have been due to the public nature of these spaces connected to educators’ real-life identities. In a follow-up interview study, Mercieca and Kelly (2018) found that private groups on Facebook were places where educators &mdash; early-career educators, even &mdash; could access peer support that was not available to them in their local school of employment.

Numerous studies of educators’ use of social media have reported professional isolation as a significant issue for teachers (Carpenter & Krutka, 2014; Carpenter, McDade, & Childers, 2018; Hur & Brush, 2009; Trust & Horrocks, 2017; Yadav, Gretter, Hambrusch, & Sands, 2016). For instance, working in a small elementary school with only one teacher per grade level (Hur & Brush, 2009) or teaching a specialized content area like computer science (Yadav et al., 2016) led educators to reason that the best opportunities to seek professional support were online. These purposes are similar to those of the school-external networks described by März and Kelchtermans (2020) in the teacher induction literature. In addition to subject- and level-specific advice, educators have also described benefitting from experiencing a sense of camaraderie through participation online (Carpenter & Krutka, 2014; Hur & Brush, 2009; Wesely, 2013).

**Interpersonal connections.** Educators (in a general sense, not specifically ECEs) regularly use social media to connect with other people, often around the world (Trust, 2012). The question of who educators connect to for professional support is not entirely new. More than 20 years ago, Borko and Putnam (1996) described how ECEs learn to teach from other educators in their initial school of employment, as well as from students, professional development workshops, and reading. Still, the affordances of social media have expanded and transformed who educators are able to connect to: supports are no longer limited to local geography, the number of educators in a school building, the number of books in the school library, or the number and type of professional development programs offered by a school district. A teacher in Hur and Brush’s (2009) study reported that she first participated on a social media platform “for lesson plan ideas and classroom management help. Now I stick with it because I enjoy reading other people's concerns, and what conditions are like in other states or countries” (p. 297). Researchers have found that teachers appreciated the ability to engage with online groups of educators for professional development without constraints due to time or geography and resulting in perspectives more diverse than would be available locally (Prestridge, 2017; Trust et al., 2016).

The literature contains numerous examples of such interpersonal connections made by educators generally through social media. In some cases, social media platforms are used to reinforce existing, local relationships. For instance, Luo and Clifton’s (2017) preservice teachers in a educator preparation course used a common Twitter hashtag for class discussions. Reich, Levinson, and Johnston (2011) assigned preservice teachers to participate in class discussions not on a private board shared only among the class, but on the National Council for the Social Studies (NCSS) Network Ning. In both cases, these social media platforms (i.e., Twitter and Ning) were used for interactions among local preservice teachers in the same course, with the added benefit of conversations being public to a larger pool of educators who could choose to join in. Differing from these course assignments in that the local component was absent, Xing and Gao (2018) studied how educators connected globally through weekly synchronous discussions organized by the Twitter hashtag #Edchat. Finally, in a rare study of ECEs’ use of social media, Smith Risser (2013) followed one new teacher’s networking and connecting with mentors through Twitter.

## Summary of the Literature

The body of research on teacher induction and the body of research on educators’ use of social media share a broad interest in educators’ professional learning. These bodies of research also both tend to approach professional learning as social, ongoing, just-in-time, and needing recontextualization. Nevertheless, these bodies of research remain almost entirely disparate. The induction literature tends to focus on formal programs and local relationships whereas the social media literature tends to focus on informal learning opportunities and expansive, potentially global interpersonal connections. Of course, there are exceptions to these generalizations. Still, neither body of research fully meets the needs of ECEs. The induction literature focuses the scope of inquiry too narrowly to include people ECEs are likely talking to and learning from already (e.g., interpersonal connections on social media). On the other hand, the social media literature leaves the scope of inquiry too broad and general by not considering that there may be unique experiences and challenges faced by new educators transitioning from preparatory to professional context. See Table 1 for a summary comparison of these two bodies of research.

Table 1

*Comparison of the Teacher Induction and Social Media Literatures*

```{r packages, include=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
```

```{r table-1, tidy=TRUE, include=TRUE, echo=FALSE}

table1 <- data.frame(
  col1 = c(
    "Supports for Professional Learning",
    "Reasons for Supports",
    "Interpersonal Connections"
  ),
  col2 = c(
    "Primarily formal induction programs (e.g., mentoring, seminars, collaborative work times), some school-external networks",
    "Induction challenges (e.g., everything is new, still learning, professional-identity formation)",
    "Primarily local relationships (e.g., mentors, peers, administrators), some school-external networks (e.g., virtual learning communities, virtual workshops)"
  ),
  col3 = c(
    "Primarily informal learning opportunities (e.g., resources, skills, curricular materials, encouragement)",
    "General difficulty of teaching (e.g., emotionally tiring, needing to look for very specific ideas, pressures to appear competent to local colleagues, professional isolation)",
    "Primarily global networks (e.g., Twitter hashtags, subreddits, Pinterest accounts), some local connections (e.g., course assignments for preservice teachers)"
  )
)

knitr::kable(table1,
             col.names=c("PLN Component", 
                         "Teacher Induction literature", 
                         "Social Media literature"
                         ),
             booktabs = TRUE) %>%
  kable_styling(full_width=TRUE) %>%
  column_spec(1, bold=TRUE, border_right=FALSE)
```

It is noteworthy that research on teacher induction has tended to focus on local connections, most often in an educator’s school of employment and sometimes at the district level. Less considered are possible connections beyond the local context, such as emailing former colleagues from an educator preparation program or finding mentors through professional societies, let alone the potentially global set of interpersonal connections through social media. On the other hand, research on educators’ use of social media notes a common theme of educators’ appreciation for diverse and far-reaching interpersonal connections in addition to more local ones. The social media literature has reported how educators are using social media to connect with both peers and those more knowledgeable than themselves, similar to the interpersonal relationships with colleagues and mentors structured by formal induction programs.

In addition, there are multiple points of connection between the informal learning opportunities educators (generally, not specifically ECEs) seek on social media and the supports offered to ECEs through formal induction programs. Both acknowledge the difficulty of the teaching profession and seek to support continuous learning that is often just-in-time, on-demand, and makes connections to experts. In this regard, social media have advantages by providing professional development that is truly just-in-time (Greenhalgh & Koehler, 2017). Although research on teacher induction tends to foreground the local and research on social media tends to focus on the global, both bodies of research do cover both local and global relationships. Because of this, the recontextualization of ideas and resources is a challenge in both bodies of research. The informal learning opportunities afforded by social media are less systematic and structured than Kang and Berliner (2012), Zhukova (2018), and others have argued induction supports should be, while formal induction programs may present solutions too general to be useful to a particular ECE.

Finally, a gap in the literature remains: research on teacher induction has not fully acknowledged the full array of interpersonal connections available to ECEs through social media today, and research on social media rarely focuses upon ECEs. This study seeks to addressed this gap in the literature, and I describe the purpose of this study in the following section.
